Large-scale spatiotemporal variation in vital rates and population dynamics of an alpine bird

### 2023-12-30 Manuscript_Nater_etal.qmd
Added text on variance decomposition results

>>>>

```{r, echo = FALSE}
# Posterior summaries
varDec.sum <- readRDS("Results/PosteriorSummaries_VarDecomp.rds")

# Printing function
printPostSum2 <- function(table, Parameter, VarComponent){

  idx <- which(table$Parameter == Parameter & table$VarComponent == VarComponent)

  print.out <- paste0(
      round(table$median[idx]*100, digits = 1), 
      " [",
      round(table$lCI[idx]*100, digits = 1),
      ", ",
      round(table$uCI[idx]*100, digits = 1),
      "]"
  )
  return(print.out)
}

# All parameter summaries
Rec_A <- printPostSum2(varDec.sum, "Recruitment", "Area")
Rec_Y <- printPostSum2(varDec.sum, "Recruitment", "Year")
Rec_R <- printPostSum2(varDec.sum, "Recruitment", "Residual")
Rec_Cov <- printPostSum2(varDec.sum, "Recruitment", "RodentOcc")

Surv_A <- printPostSum2(varDec.sum, "Survival", "Area")
Surv_Y <- printPostSum2(varDec.sum, "Survival", "Year")
Surv_R <- printPostSum2(varDec.sum, "Survival", "Residual")

Det_A <- printPostSum2(varDec.sum, "Detection", "Area")
Det_Y <- printPostSum2(varDec.sum, "Detection", "Year")
Det_R <- printPostSum2(varDec.sum, "Detection", "Residual")
```

The relative importance of different components for explaining parameter variation differed among recruitment rate, survival probability, and detection decay (@fig-varDecomp).
The largest portion of variation in recruitment was attributed to residual variation (`r Rec_R` %), followed by spatial (`r Rec_A` %) and temporal (`r Rec_Y` %) variation. Rodent occupancy, which contains both a spatial and a temporal dimension, explained `r Rec_Cov` % of the total variation. 
For survival, there was large uncertainty in the estimated proportions of variance explained by different components. The model predicted similar potential contributions from temporal (`r Surv_Y` %) and residual (`r Surv_R` %) variation and suggested that spatial variation was only responsible for `r Surv_A` % of the total variance. 
Total variance in detection decay was attributed evenly to spatial, temporal, and residual variation at `r Det_A` %, `r Det_Y` %, and `r Det_R` %, respectively.

![Posterior distributions for the proportions of parameter variance explained by spatial (blue), temporal (orange), and residual (green) variation, as well as by effects of rodent occupancy (yellow).](Figures/VarDecomposition_overall.png){#fig-varDecomp}
